---
title: "Ruoruo_test1"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
require("knitr")
library(ggplot2)
library(ggrepel)
library(cowplot)
library(plyr)

#for color
# Install
#install.packages("wesanderson")
# Load
library(wesanderson)

opts_knit$set(root.dir = "/Users/shan/Documents/Rourou_test/test1/")
```


## Figure 1

lines with different n 
input format 
n eps(x) result(y)

```{r}
#read data (result_test.txt)
data1 <- read.table('result/result_test.txt',header =T, na.string = 'NA')
data1$n <- factor(data1$n)

p <- ggplot(data1,aes(x=data1$x,y=data1$y,color = n)) +
  geom_point() + 
  geom_line() +
  scale_x_continuous(breaks = seq(0, 1, 0.1)) +
  scale_y_continuous(limits = c(0, 5)) + 
  #xlab("\u03B5") + 
  xlab(expression(epsilon)) + 
  ylab("value") + 
  theme(panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(size = 0.5, linetype = "solid"),
        panel.background = element_rect(fill = "white"))
p
#ggsave("Fig1_test.pdf", plot = p,  scale = 0.65, width = 8, height = 5.5, dpi = 300)
save_plot("Fig1_test.pdf", 
            p,
            base_height = 5*1, 
            base_width = 7*1)
```
## Figure 2

<http://blog.sciencenet.cn/blog-3406804-1155528.html>
Follow the method for PCoA analysis
input format
Sample group x y
color reference <https://github.com/karthik/wesanderson>
wes_palettes <- list(
  BottleRocket1 = c("#A42820", "#5F5647", "#9B110E", "#3F5151", "#4E2A1E", "#550307", "#0C1707"),
  BottleRocket2 = c("#FAD510", "#CB2314", "#273046", "#354823", "#1E1E1E"),
  Rushmore1 = c("#E1BD6D", "#EABE94", "#0B775E", "#35274A" ,"#F2300F"),
  Rushmore = c("#E1BD6D", "#EABE94", "#0B775E", "#35274A" ,"#F2300F"),
  Royal1 = c("#899DA4", "#C93312", "#FAEFD1", "#DC863B"),
  Royal2 = c("#9A8822", "#F5CDB4", "#F8AFA8", "#FDDDA0", "#74A089"),
  Zissou1 = c("#3B9AB2", "#78B7C5", "#EBCC2A", "#E1AF00", "#F21A00"),
  Darjeeling1 = c("#FF0000", "#00A08A", "#F2AD00", "#F98400", "#5BBCD6"),
  Darjeeling2 = c("#ECCBAE", "#046C9A", "#D69C4E", "#ABDDDE", "#000000"),
  Chevalier1 = c("#446455", "#FDD262", "#D3DDDC", "#C7B19C"),
  FantasticFox1 = c("#DD8D29", "#E2D200", "#46ACC8", "#E58601", "#B40F20"),
  Moonrise1 = c("#F3DF6C", "#CEAB07", "#D5D5D3", "#24281A"),
  Moonrise2 = c("#798E87", "#C27D38", "#CCC591", "#29211F"),
  Moonrise3 = c("#85D4E3", "#F4B5BD", "#9C964A", "#CDC08C", "#FAD77B"),
  Cavalcanti1 = c("#D8B70A", "#02401B", "#A2A475", "#81A88D", "#972D15"),
  GrandBudapest1 = c("#F1BB7B", "#FD6467", "#5B1A18", "#D67236"),
  GrandBudapest2 = c("#E6A0C4", "#C6CDF7", "#D8A499", "#7294D4"),
  IsleofDogs1 = c("#9986A5", "#79402E", "#CCBA72", "#0F0D0E", "#D9D0D3", "#8D8680"),
  IsleofDogs2 = c("#EAD3BF", "#AA9486", "#B6854D", "#39312F", "#1C1718")
)

```{r}
##function to move the axis to custermized positions
shift_axis <- function(p, x=0, y=0){
  g <- ggplotGrob(p)
  dummy <- data.frame(x=x, y=y)
  ax <- g[["grobs"]][g$layout$name == "axis-b"][[1]]
  bx <- g[["grobs"]][g$layout$name == "axis-l"][[1]]
  p + annotation_custom(grid::grobTree(ax, vp = grid::viewport(y=1, height=sum(ax$height))), ymax=y, ymin=y) +
    annotation_custom(grid::grobTree(bx, vp = grid::viewport(x=1, width=sum(bx$width))), xmax=x, xmin=x) +
    geom_hline(aes(yintercept=y), data = dummy) +
    geom_vline(aes(xintercept=x), data = dummy) +
    theme(axis.line = element_blank(),
          axis.text.x = element_blank(), 
          axis.text.y = element_blank(),
          axis.ticks.x= element_blank(),
          axis.ticks.y= element_blank())
}

```

```{r}
#test for a single round 0

#read data (result_test.txt)
point <- read.table('result3/0_centroids.txt',header =T, na.string = 'NA')
point$group <- factor(point$group)

#read A group border file
group_borderA <- read.table('result3/0_A_polygon.txt',header =T, na.string = 'NA')
group_borderA$group <- factor(group_borderA$group)

#read B group border file
group_borderB <- read.table('result3/0_B_polygon.txt',header =T, na.string = 'NA')
group_borderB$group <- factor(group_borderB$group)

pA <- ggplot(point, aes(x,y)) +
  geom_polygon(data=group_borderA,aes(fill = group, group = group), alpha=0.3) +
  geom_point(aes(color = group), size = 3) + 
  scale_color_manual(values=c('#FF0000', '#00A08A', '#5BBCD6', '#F2AD00')) +
  scale_fill_manual(values=c('#FF0000', '#00A08A', '#5BBCD6', '#F2AD00')) + 
  #annotate('text', label = 'A', x = -0.3, y = 0.06, size = 5, colour = '#f8766d') +
  #annotate('text', label = 'B', x = 0.15, y = 0.35, size = 5, colour = '#00ba38') +
  #annotate('text', label = 'C', x = 0.26, y = -0.13, size = 5, colour = '#619cff') +
  #xlab(expression(epsilon)) + 
  #ylab("value") 
  xlim(c(-2.5,2.5)) +
  ylim(c(-2.5,2.5)) +
  theme(legend.position="none")

pA_modify <-  shift_axis(pA, 0, 0)
#pA_modify 
#ggsave('Fig2_A_test.pdf', pA_modify, width = 7, height = 6)

pB <- ggplot(point, aes(x,y)) +
  geom_polygon(data=group_borderB,aes(fill = group, group = group), alpha=0.3) +
  geom_point(aes(color = group), size = 3) + 
  scale_color_manual(values=wes_palette(n=4, name="Darjeeling1")) +
  scale_fill_manual(values=wes_palette(n=4, name="Darjeeling1")) + 
  #annotate('text', label = 'A', x = -0.3, y = 0.06, size = 5, colour = '#f8766d') +
  #annotate('text', label = 'B', x = 0.15, y = 0.35, size = 5, colour = '#00ba38') +
  #annotate('text', label = 'C', x = 0.26, y = -0.13, size = 5, colour = '#619cff') +
  #xlab(expression(epsilon)) + 
  #ylab("value") 
  xlim(c(-2.5,2.5)) +
  ylim(c(-2.5,2.5)) +
  theme(legend.position="none")

pB_modify <-  shift_axis(pB, 0, 0)
#pB_modify 

# now add the title
title <- ggdraw() + draw_label("Plots for 0", fontface='bold')
pAll <- plot_grid(pA_modify, pB_modify, labels = c("A","B"), ncol = 2)
pAll <- plot_grid(title, pAll, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins

pAll
ggsave('Fig2_test.pdf', pAll, width = 6*2, height = 6)

```
```{r}
list = seq(0,28,1)
#list <- c(0,1,2,3,4,5,6,7,8,9,10,11,12,14,15,17,18,19,21,22,23,24,25,27,28)
for (i in list){
  #define input and output files
  filePoint = paste("result3/",i,"_centroids.txt",sep='')
  filePointNext= paste("result3/",i+1,"_centroids.txt",sep='')
  fileA = paste("result3/",i,"_A_polygon.txt",sep='')
  fileB = paste("result3/",i,"_B_polygon.txt",sep='')
  ResFig = paste("Figure/Fig_",i,".png",sep='')
  
  #check 
  #print(file_point)
  #print(fileA)
  #print(fileB)
  #print(ResFig)
  
  #read center point file
  point <- read.table(filePoint, header =T, na.string = 'NA')
  point$group <- factor(point$group)
  
  #read center point file
  poinNext <- read.table(filePointNext, header =T, na.string = 'NA')
  poinNext$group <- factor(poinNext$group)

  #read A group border file
  group_borderA <- read.table(fileA, header =T, na.string = 'NA')
  group_borderA$group <- factor(group_borderA$group)

  #read B group border file
  group_borderB <- read.table(fileB, header =T, na.string = 'NA')
  group_borderB$group <- factor(group_borderB$group)

  pA <- ggplot(point, aes(x,y)) +
    geom_polygon(data=group_borderA,aes(fill = group, group = group), alpha=0.3) +
    geom_point(aes(color = group), size = 3) + 
    geom_point(data = poinNext, aes(x,y,color = group), size = 9, shape='+') + 
    scale_color_manual(values=c('#FF0000', '#00A08A', '#5BBCD6', '#F2AD00')) +
    scale_fill_manual(values=c('#FF0000', '#00A08A', '#5BBCD6', '#F2AD00')) + 
    xlab("") + 
    ylab("") +
    xlim(c(-2.5,2.5)) +
    ylim(c(-2.5,2.5)) +
    theme(legend.position="none")
  pA_modify <-  shift_axis(pA, 0, 0)
  
  pB <- ggplot(point, aes(x,y)) +
    geom_polygon(data=group_borderB,aes(fill = group, group = group), alpha=0.3) +
    geom_point(aes(color = group), size = 3) + 
    geom_point(data = poinNext, aes(x,y,color = group), size = 9, shape='+') + 
    scale_color_manual(values=c('#FF0000', '#00A08A', '#5BBCD6', '#F2AD00')) +
    scale_fill_manual(values=c('#FF0000', '#00A08A', '#5BBCD6', '#F2AD00')) + 
    xlab("") + 
    ylab("") +
    xlim(c(-2.5,2.5)) +
    ylim(c(-2.5,2.5)) +
    theme(legend.position="none")
  pB_modify <-  shift_axis(pB, 0, 0)
  
  # now add the title
  label_sample = paste("Plots for ",i,sep='') 
  title <- ggdraw() + draw_label(label_sample, fontface='bold')
  pAll <- plot_grid(pA_modify, pB_modify, labels = c("A","B"), ncol = 2)
  pAll <- plot_grid(title, pAll, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title 
  
  pAll
  ggsave(ResFig, pAll, width = 3*2, height = 3)
}


```

